\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2022-02-04 manuscript.Rmd
Parallel Analysis is Excluded

```{r ParallelEFA, include=FALSE}
#This chunk holds code for factor identification method : Horn
# Parallel analysis
Horn <- paran(correlations$rho, iterations=500, centile=0, quietly=FALSE,
           status=TRUE, all=FALSE, cfa=FALSE, graph=TRUE,
           color=TRUE, col=c("black","red","blue"),
           lty=c(1,2,3), lwd=1, legend=TRUE, 
           width=640, height=640, grdevice=png, seed=0, mat=NA, n=NA)

@@

write.csv(full.map, "Table_raw/map_stat.csv")
```
Scree plot ( Figure \@ref(fig:facIdFig)) suggested a six-factor solution. Horn's parallel analysis [@hornRationaleTestNumber1965] with 500 iterations also indicated a six-factor solution. However, the minimum average partial (MAP) method (Table \@ref(tab:factormp)) [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:facIdFig)) suggested a five-factor solution. As a result, we tested both five-factor and six-factor solutions.
```{r factors, include=F}
#This chunk holds code for compiled factor identification plots

fator <- cowplot::plot_grid(parallel, scree.plot,Hull, 
                   labels = "AUTO",
                   ncol=1, 
                  align = "v", 
                  label_fontfamily = "Arial",
                  label_fontface = "plain")
ggsave("Manuscript.figures/factors.png",fator, width = 5, height = 7, dpi = 600)
```

@@

(ref:facIdFig) Factor Identification Methods (A) Parallel analysis  indicated the optimal number of factors were six. (B) Scree plot suggested six factors. (C) Hull method indicated 5 factors were required to balance the model fit and number of parameters.

>>>>

```{r ParallelEFA, eval=FALSE, include=FALSE}
#This chunk holds code for factor identification method : Horn
# Parallel analysis
Horn <- paran(correlations$rho, iterations=500, centile=0, quietly=FALSE,
           status=TRUE, all=FALSE, cfa=FALSE, graph=TRUE,
           color=TRUE, col=c("black","red","blue"),
           lty=c(1,2,3), lwd=1, legend=TRUE, 
           width=640, height=640, grdevice=png, seed=0, mat=NA, n=NA)

@@

write.csv(full.map, "Table_raw/map_stat.csv")
```
Scree plot ( Figure \@ref(fig:facIdFig)) suggested a six-factor solution. However, the minimum average partial (MAP) method (Table \@ref(tab:factormp)) [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:facIdFig)) suggested a five-factor solution. As a result, we tested both five-factor and six-factor solutions.
```{r factors, include=F}
#This chunk holds code for compiled factor identification plots

fator <- cowplot::plot_grid(scree.plot,Hull, 
                   labels = "AUTO",
                   ncol=1, 
                  align = "v", 
                  label_fontfamily = "Arial",
                  label_fontface = "plain")
ggsave("Manuscript.figures/factors.png",fator, width = 5, height = 7, dpi = 600)
```

@@

(ref:facIdFig) Factor Identification Methods  (A) Scree plot suggested six factors. (B) Hull method indicated 5 factors were required to balance the model fit and number of parameters.
